### 2014-11-12 Docs/introduction/introduction.tex
add the notation needed for the flowchart from the multilevel paper
update ref

\noindent We have several papers that describe applications of the
method to Type Ia supernovae, X-ray bursts, and stellar evolution:
\begin{itemize}
\item {\em Multidimensional Modeling of Type I X-ray Bursts,}
  C. M. Malone, A. Nonaka, A. S. Almgren, J. B. Bell, \& M. Zingale 2011,
  ApJ, 728, 118 (henceforth ``the XRB paper'')
\item {\em The Convective Phase Preceding Type Ia Supernovae,}
  M. Zingale, A. S. Almgren, J. B. Bell, C. M. Malone, A. Nonaka, \& S. E. Woosley 2011, ApJ,
  740, 8 (henceforth paper V)
\item {\em High-Resolution Simulations of Convection Preceding Ignition in
  Type Ia Supernovae Using Adaptive Mesh Refinement,}
  A. Nonaka, M. Zingale, A. J. Aspden, A. S. Almgren, J. B. Bell, \& S. E. Woosley 2012, 
  ApJ, 745, 73
\item {\em Low Mach Number Modeling of Convection in Helium Shells on
  Sub-Chandrasehkar White Dwarfs. I. Methodology,} M.~Zingale,
  A.~Nonaka, A.~S.~Almgren, J.~B.~Bell, C.~M.~Malone, \&
  R.~J.~Orvedahl 2013, ApJ, 764, 97
\item {\em Low-Mach Number Modeling of Core Convection in Massive Stars,}
  C.~Gilet, A.~S.~Almgren, J.~B.~Bell, A.~Nonaka, S.~E.~Woosley, \& M. Zingale
  2013, ApJ, 773, 137
\end{itemize}

>>>>

\noindent We have several papers that describe applications of the
method to Type Ia supernovae, X-ray bursts, and stellar evolution:
\begin{itemize}
\item {\em Multidimensional Modeling of Type I X-ray Bursts,}
  C. M. Malone, A. Nonaka, A. S. Almgren, J. B. Bell, \& M. Zingale 2011,
  ApJ, 728, 118 (henceforth ``the XRB paper'')

\item {\em The Convective Phase Preceding Type Ia Supernovae,}
  M. Zingale, A. S. Almgren, J. B. Bell, C. M. Malone, A. Nonaka, \& S. E. Woosley 2011, ApJ,
  740, 8 (henceforth paper V)

\item {\em High-Resolution Simulations of Convection Preceding Ignition in
  Type Ia Supernovae Using Adaptive Mesh Refinement,}
  A. Nonaka, M. Zingale, A. J. Aspden, A. S. Almgren, J. B. Bell, \& S. E. Woosley 2012, 
  ApJ, 745, 73

\item {\em Low Mach Number Modeling of Convection in Helium Shells on
  Sub-Chandrasehkar White Dwarfs. I. Methodology,} M.~Zingale,
  A.~Nonaka, A.~S.~Almgren, J.~B.~Bell, C.~M.~Malone, \&
  R.~J.~Orvedahl 2013, ApJ, 764, 97

\item {\em Low-Mach Number Modeling of Core Convection in Massive Stars,}
  C.~Gilet, A.~S.~Almgren, J.~B.~Bell, A.~Nonaka, S.~E.~Woosley, \& M. Zingale
  2013, ApJ, 773, 137

\item {\em Multidimensional Modeling of Type I X-ray Bursts. II. Two-Dimensional 
       Convection in a Mixed H/He Accretor,}
   C.~M.~Malone, M.~Zingale, A.~Nonaka, A.~S.~Almgren, \& J.~B.~Bell 2014, ApJ, 788, 115

\item {\it Comparisons of Two- and Three-Dimensional Convection in Type I X-ray Bursts} 
M.~Zingale, C.~M.~Malone, A.~Nonaka, A.~S.~Almgren, \& J.~B.~Bell 
submitted to ApJL.

\end{itemize}
